\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-29 Report/project_report.tex
Cleaned up MSCKF triangulation math notation

[BATCH MATH GOES HERE?]

@@

\subsection{Feature Position Estimation}
When a feature $f_j$ goes out of view of the camera, the MSCKF generates a batch-optimized estimate $\hat{\Vec{p}}_G^{f_j G}$ of the feature's position in the global frame.

>>>>

\begin{equation}
(\Vec H^T \Vec T ^{-1} \Vec H ) \delta \Vec{x}^*  = - \Vec{H}^T\Vec{T}^{-1}\Vec{e}(\bar{\Vec{x}})
\end{equation}

\begin{equation}
\delta\Vec{x} := \bbm \delta \Vec x_0 \\ \vdots \\ \delta \Vec x_K \\ \delta \Vec f_1 \\ \vdots \\ \delta \Vec f_N\ebm,
\end{equation}
where $N$ is the number of unique features observed in the window and 
\begin{equation}
\mathbf{H} := \left[\begin{array}{cccccc}
 -\Vec H_{\Vec x, 1} & \Vec 1 & &  & &   \\ 
 & -\Vec G_{\Vec x, 1} &  &  &  &   -\Vec G_{\Vec f, 1} \\ \hline
 & -\Vec H_{\Vec x, 2} & \Vec 1 & & &    \\ 
 & & -\Vec G_{\Vec x, 2} &  & &  -\Vec G_{\Vec f, 2}   \\ \hline
 &  & \ddots & \ddots & & \vdots  \\  \hline
  & & & -\Vec H_{\Vec x, K} & \Vec 1 & \\ 
 & & & & -\Vec G_{\Vec x, K} &  -\Vec G_{\Vec f, K}   \\  
\end{array}\right], 
\end{equation},

\begin{equation}
\Vec G_{\Vec{x}, k}^j := \pd{\Vec g}{ \Vec p}\Bigr|_{\Vec p = \bar{\Vec p}_{c_k}^{p_j c_k}} \bbm -\Vec C_{cv} \Vec C_{v_k i} & \Vec C_{cv} (\Vec C_{v_k i} (\boldsymbol{\rho}_i^{p_j i} - \Vec r_i^{v_k i} ) )^\times  \ebm\end{equation}

\begin{equation}
\quad \Vec G_{\Vec x, k} := \bbm \Vec G_{\Vec x, k}^1 \\ \vdots \\ \Vec G_{\Vec x, k}^M \ebm
\end{equation}

\begin{equation}
\Vec G_{\Vec f, k}^j := \pd{\Vec g}{ \Vec p}\Bigr|_{\Vec p = \bar{\Vec p}_{c_k}^{p_j c_k}} \bbm \Vec C_{cv} \Vec C_{v_k i}\ebm\end{equation}

\begin{equation}
\quad \Vec G_{\Vec f, k} := \underbrace{\bbm \Vec G_{\Vec f, k}^1 & & \\ & & \Vec G_{\Vec f, k}^2 & \\ & & \vdots &  \\ & & & \Vec G_{\Vec f, k}^M \ebm}_{\text{$j$th block column position given by feature id $n$}} \in \Real^{4M \times 3N}
\end{equation}

and,
\begin{equation}
\bar{\Vec p}_{c_k}^{p_j c_k} := \bbm x \\ y \\ z \ebm = \Vec C_{cv} \left( \Vec C_{v_k i} (\boldsymbol{\rho}_i^{p_j i} - \Vec r_i^{v_k i} )   - \boldsymbol \rho_v^{cv} \right),
\end{equation}

\begin{equation}
\pd{\Vec g}{ \Vec p}\Bigr|_{\Vec p = \bar{\Vec p}_{c_k}^{p_j c_k}} = \bbm \frac{f_u}{z} & 0 & -\frac{1}{z^2} f_u x \\  0 & \frac{f_v}{z} & -\frac{1}{z^2} f_v y  \\ \frac{f_u}{z} & 0 & -\frac{1}{z^2} f_u (x-b) \\  0 & \frac{f_v}{z} & -\frac{1}{z^2} f_v y\ebm.
\end{equation}
or for monocular,
\begin{equation}
\pd{\Vec g}{ \Vec p}\Bigr|_{\Vec p = \bar{\Vec p}_{c_k}^{p_j c_k}} = \bbm \frac{f_u}{z} & 0 & -\frac{1}{z^2} f_u x \\  0 & \frac{f_v}{z} & -\frac{1}{z^2} f_v y \ebm.
\end{equation}

@@

\subsection{Feature Position Estimation}
When a feature $f_j$ goes out of view of the camera, the MSCKF estimates its position $\hat{\Vec{p}}_G^{f_j G}$ using an inverse-depth least-squares Gauss-Newton optimization. 
The procedure takes as input $N$ camera poses and $N$ sets of ``ideal'' pixel measurements, where ``ideal'' means that the pixel measurements have been corrected for the camera intrinsics:
\begin{align}
\hat{\Vec{z}}_i^{(j)} &= \bbm u'_i & v'_i \ebm ^T = \bbm (u_i - c_u)/f_u & (v_i - c_v)/f_v \ebm ^T
\end{align}
We initialize the optimization by estimating the position of feature $f_j$ in camera frame $C_1$ using a linear least squares method with measurements from the first two camera frames, $C_1$ and $C_2$:
\begin{align}
\hat{\Vec{p}}_{C_1}^{f_j C_1} := \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & \hat{Z}^{(j)}_{C_1} \ebm ^T = \lambda \boldsymbol{\rho}_{C_1}^{f_j}
\end{align}
where
\begin{align}
\boldsymbol{\rho}_{C_i}^{f_j} &:= \frac{1}{\sqrt{u'^2_i + v'^2_i + 1}}\bbm u'_i & v'_i & 1\ebm^T
\end{align}
and
\begin{align}
\lambda &= \left[(\Vec A^T \Vec A)^{-1} \Vec A^T \hat{\Vec{p}}_{C_1}^{C_2 C_1} \right]_1
\end{align}
with
\begin{align}
\Vec A &:= \bbm \boldsymbol{\rho}_{C_1}^{f_j} & -\boldsymbol{\rho}_{C_2}^{f_j} \ebm.
\end{align}

Next, we define a vector of three parameters:
\begin{align}
\hat{\Vec{y}} &= \bbm \alpha & \beta & \gamma \ebm^T = \frac{1}{\hat{Z}^{(j)}_{C_1}} \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & 1 \ebm ^T
\end{align}
The feature position in camera frame $C_i$ can be expressed as
\begin{align}
\hat{\Vec{p}}_{C_i}^{f_j C_i} = \hat{\Vec{C}}_{i1} \hat{\Vec{p}}_{C_1}^{f_j C_1}  + \hat{\Vec{p}}_{C_i}^{C_1 C_i}
\end{align}
With our state parameters, we can use this equation to define three functions:
\begin{align}
    \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \\ h_3 (\hat{\Vec{y}}) \ebm 
    & = \hat{\Vec{C}}_{i1} \bbm \alpha \\ \beta \\ 1 \ebm + \gamma  \hat{\Vec{p}}_{C_i}^{C_1 C_i} \notag \\
    & = \bbm C_{11} \alpha + C_{12} \beta + C_{13} + \gamma \hat{x}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{21} \alpha + C_{22} \beta + C_{23} + \gamma \hat{y}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{31} \alpha + C_{32} \beta + C_{33} + \gamma \hat{z}_{C_i}^{C_1 C_i} 
        \ebm 
\end{align}
The camera measurement error can then be written as
\begin{align}
\Vec e(\hat{\Vec{y}}) = \hat{\Vec{z}}_i^{(j)} - \frac{1}{h_3 (\hat{\Vec{y}}) } \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \ebm
\end{align}
The least squares linear system then becomes
\begin{align}
(\Vec  E^T \Vec W ^{-1} \Vec E ) \delta \Vec{y}^*  = - \Vec{E}^T\Vec{W}^{-1}\Vec{e}(\hat{\Vec{y}})
\end{align}
where
\begin{align}
\Vec E &= \frac{\partial \Vec e}{\partial \hat{\Vec{y}}}
& &
\text{and}
&
\Vec W &= \bbm \Vec{R}_1^{(j)} & & \\ & \ddots & \\ & & \Vec{R}_N^{(j)} \ebm 
\end{align}
with $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_u, \sigma^2_v\right\}$.

The Jacobian elements are given by
\begin{align}
\frac{\partial \Vec e}{\partial \alpha} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \alpha} h_3 + \frac{\partial h_3}{\partial \alpha} h_1 \\[0.5em]
                        -\frac{\partial h_2}{\partial \alpha} h_3 + \frac{\partial h_3}{\partial \alpha} h_2 \ebm
\\[0.5em]
\frac{\partial \Vec e}{\partial \beta} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \beta} h_3 + \frac{\partial h_3}{\partial \beta} h_1 \\[0.5em] 
                        -\frac{\partial h_2}{\partial \beta} h_3 + \frac{\partial h_3}{\partial \beta} h_2 \ebm
\\[0.5em]
\frac{\partial \Vec e}{\partial \gamma} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \gamma} h_3 + \frac{\partial h_3}{\partial \gamma} h_1 \\[0.5em] 
                        -\frac{\partial h_2}{\partial \gamma} h_3 + \frac{\partial h_3}{\partial \gamma} h_2 \ebm
\end{align}
with
\begin{align}
\frac{\partial h_1}{\partial \alpha} &= C_{11}, & \frac{\partial h_1}{\partial \beta} &= C_{12}, & \frac{\partial h_1}{\partial \gamma} &= \hat{x}_{C_i}^{C_1 C_i} \notag \\
\frac{\partial h_2}{\partial \alpha} &= C_{21}, & \frac{\partial h_2}{\partial \beta} &= C_{22}, & \frac{\partial h_2}{\partial \gamma} &= \hat{y}_{C_i}^{C_1 C_i} \\
\frac{\partial h_3}{\partial \alpha} &= C_{31}, & \frac{\partial h_3}{\partial \beta} &= C_{32}, & \frac{\partial h_3}{\partial \gamma} &= \hat{z}_{C_i}^{C_1 C_i} \notag .
\end{align}
